Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)

### 2025-02-07 products/manuscript/Manuscript.qmd
fix errors when rendering the word file

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

The raw data import and cleaning will be conducted seprately since the dataset is large.

>>>>

## Data import and cleaning
Since the dataset for this project is too large to upload to GitHub, I reduced its size and saved the smaller version as an RDS file, treating it as the raw data. Here's the code I used to reduce size:

 # load packages
 library(here)
 library(dplyr)
 # load raw data
 LCAraw1 <- read.csv(here("data", "raw-data", "LCA2020to2024.csv"))
 # Shrink the data
 colnames(LCAraw1)
 LCAraw <- LCAraw1 %>%
   select(CASE_STATUS, VISA_CLASS, RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE,   WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE)
 # Save as rds
 save_data_location <- here::here("data","raw-data","LCAraw.rds")
 saveRDS(LCAraw, file = save_data_location)

```{r}
# load packages
library(here)
library(dplyr)

# load raw data
LCAraw <- readRDS(here("data", "raw-data", "LCAraw.rds"))

# get the overview of the data
dim(LCAraw)
head(LCAraw)

# Keep only the certified case and H-1B visa, and remove these two column
LCAdata <- LCAraw %>%
  filter(CASE_STATUS == "Certified", VISA_CLASS == "H-1B")%>%
  select(RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE)

# take a look at the processed data
dim(LCAdata)
head(LCAdata)

```
